Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-05 Paper/paperN.tex

The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped onto text to give a semantic representation. But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing. An automatic system could provide more complete descriptions of frames in current document banks and could better adapt to new words and evolving meanings.

In this project we investigate whether probabilistic latent-variable models can cluster verbs based on their meaning, which is inferred from the arguments with which it occurs. These clusters then make up a broader, but hopefully distinct, meaning. The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles. The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context. Hence the broader meaning is latent. To evaluate our models we use two metrics, one of which uses framenet data to check whether the induced frames are similar to clusters of verbs in framenet, the other to check whether the resulting frames are coherent, i.e. whether the found clusters are not completely random. See section \ref{results} for more detail.

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximization on a simple co-occurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occurring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames. This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

A syntactic-ngram is a $k$-word rooted subtree of some sentence.
Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
books and labeled with Penn Treebank part-of-speech tags Stanford-basic dependency 
labels \citep{ngrams2013}.
Each ngram also includes frequency counts by year.

This project uses the verbargs subeset (130M items) of Google syntactic-ngrams.
An ngram in the verbargs dataset consist of a verb and all of its 
immediate arguments.
We considered only the VSO's in this dataset, that is; we pruned verbargs to
those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
is the ngram's root verb (1.6M items, 96M by count). 
We further trimmed the data to consider only the \%25 most common verbs 
(800K items, 78M by count).

@@

The $\alpha$ and $\beta$ hyperparameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem. We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$. The grid search builds, for each possible parameter set, a model which is evaluated on the cross validation set. The highest scoring model is tested with the test set. We ran grid search for model 0 on $50$ - $200$ frames, with steps of $50$, and $\alpha$ of $0.1, 0.5, 1, 1.5$, and $2$. The grid search for Model 1 was the the same, additionally testing $\beta$ across the same values as $\alpha$
\section{Results}
\label{results}

\subsection{Frame Coherency}
Verb clusters are based on the arguments with which they occurring in the data. So to test how well the models perform on clustering, the probability that the model generates a triple from the testset, should be greater than this triple with a random verb in place of the real one. This metric is the same as the one used by \citeauthor{rooth1999}. More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
The results are percentages of data points which satisfy this condition. Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probability is low. Furthermore, one can assume that the occurrences of same frame assignment cancel each other out, i.e. the random triple has higher probability than the real one as many times as vice versa.

@@

%Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
\section{Results}
These results are experimental, i.e. the parameters are guessed and therefor probably not optimal. (Since gridsearchis more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
\begin{table}[h]
\begin{tabular}{|l||c|c|}
  \hline
  &dicesim&coherencey\\
  \hline
  \hline
  model 0& 0.28&19\%  \\
  \hline
  model 1&0.29 &71\%  \\
  \hline
\end{tabular}
\caption{results}
\label{results}
\end{table}

@@

More generally, VSO models don't take full advantage of the various kinds of argumens
in the verbargs dataset. 
As we have seen, only a fraction of verbs actually occur as part of a VSO subtree.
By considering only VSOs, we may introduce some bias in the frames that we can induce,
since frames with particular role configurationts (such as \emph{agent, patient}) may
lend themselves better to transitive verbs.

@@

\section{Conclusion}

\section*{Who did what}
We all tried to work as much as possible and necessary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid search). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody.

>>>>

The FrameNet project \citep{FrameNet} is an ongoing manual effort to define frames which could be mapped onto text to give a semantic representation. But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing. An automatic system could provide more complete descriptions of frames in current document banks and could better adapt to new words and evolving meanings.

In this project we investigate whether probabilistic latent-variable models can cluster verbs based on their meaning, which is inferred from the arguments with which it occurs. These clusters then make up a broader, but hopefully distinct, meaning. The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles. The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context. Hence the broader meaning is latent. To evaluate our models we use two metrics, one of which uses FrameNet data to check whether the induced frames are similar to clusters of verbs in FrameNet, the other to check whether the resulting frames are coherent, i.e. whether the found clusters are not completely random. See section \ref{results} for more detail.

%\section{Related Work}
We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}. In the first article clustering is realized by applying expectation maximalization on a simple co-occurance model. This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns. Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples. A triple is assigned to the frame for which is probability of occurring is highest. We will use this model as our baseline (as in the O'Connor paper). The second paper covers two additional models, of which we implemented one. This model differs from the baseline model by introducing the assumption that a document generates sentences from a restricted set of frames. This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames. In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

@@

A syntactic-ngram is a $k$-word rooted sub-tree of some sentence.
Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
books and labeled with Penn Treebank part-of-speech tags Stanford-basic dependency 
labels \citep{ngrams2013}.
Each ngram also includes frequency counts by year.

This project uses the verbargs subset (130M items) of Google syntactic-ngrams.
An ngram in the verbargs dataset consist of a verb and all of its 
immediate arguments.
We considered only the VSO's in this dataset, that is; we pruned verbargs to
those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
is the ngram's root verb (1.6M items, 96M by count). 
We further trimmed the data to consider only the \%25 most common verbs 
(800K items, 78M by count).

@@

The $\alpha$ and $\beta$ hyper-parameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem. We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$. The grid search builds, for each possible parameter set, a model which is evaluated on the cross validation set. The highest scoring model is tested with the test set. We ran grid search for model 0 on $50$ - $200$ frames, with steps of $50$, and $\alpha$ of $0.1, 0.5, 1, 1.5$, and $2$. The grid search for Model 1 was the the same, additionally testing $\beta$ across the same values as $\alpha$
\section{Results}
\label{results}

\subsection{Frame Coherency}
Verb clusters are based on the arguments with which they occurring in the data. So to test how well the models perform on clustering, the probability that the model generates a triple from the test-set, should be greater than this triple with a random verb in place of the real one. This metric is the same as the one used by \citeauthor{rooth1999}. More formally: for a data-point $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
The results are percentages of data-points which satisfy this condition. Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probability is low. Furthermore, one can assume that the occurrences of same frame assignment cancel each other out, i.e. the random triple has higher probability than the real one as many times as vice versa.

@@

%Frame correctness: for the top 25 most probable verbs per frame $TV$ and FrameNet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
\section{Results}
These results are experimental, i.e. the parameters are guessed and therefor probably not optimal. (Since grid-search is more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
\begin{table}[h]
\centering
\begin{tabular}{|l||c|c|}
  \hline
  &dicesim&coherency\\
  \hline
  \hline
  model 0& 0.28&19\%  \\
  \hline
  model 1&0.29 &71\%  \\
  \hline
\end{tabular}
\caption{results}
\label{results}
\end{table}

@@

More generally, VSO models don't take full advantage of the various kinds of arguments
in the verbargs dataset. 
As we have seen, only a fraction of verbs actually occur as part of a VSO subtree.
By considering only VSOs, we may introduce some bias in the frames that we can induce,
since frames with particular role configurations (such as \emph{agent, patient}) may
lend themselves better to transitive verbs.

@@

\section{Conclusion}
Model 1 did find clusters of verbs of which the meaning can be covered by 1 predicate. Although the induced frames have often vague or broad meaning the approach works well if data is abundant. The improvement of model 1 on model 0 has a significant effect and implicates even better results can be acquired by further improvements. The kind of clustering done by these models, with opposites assigned to the same frame, can be useful for automatic stock trading systems if implemented with sentiment analysis to split on opposites. The frames are too vague to use for summarizations though.

\section*{Who did what}
We all tried to work as much as possible and necessary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid-search). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody.
